### 2025-06-19 actuarial.qmd
20241016 - render the figure caption as alt text
20250308 - citations
20250619 - calibration accuracy of projections

Here is a video of sports pundits, Stephen A. Smith and Skip Bayless, making bold statements and incorrect predictions:

![Video of Sports Pundits, Stephen A. Smith and Skip Bayless, Making Bold Statements and Incorrect Predictions. From: <https://www.youtube.com/watch?v=lTjBuEPcLlc>.](images/sportsPundits.mp4){width=100%}

@@

Another reason why judgment methods are more widely used than actuarial methods is that so-called "experts" (and people in general) show [overconfidence](#sec-cognitiveBiasesOverconfidence) in their predictions—clinicians, experts, and humans in general think they are more accurate than they actually are.
We see this when examining their calibration; their predictions tend to be miscalibrated.
For example, things they report with 80% confidence occur less than 80% of the time, an example of [overprecision](#sec-cognitiveBiasesOverconfidence) in their predictions.
Humans will sometimes be correct by chance, and they tend to mis-attribute that to their skill; humans tend to remember the successes and forget the failures.

>>>>

@TPS2017 provides a video of sports pundits, Stephen A. Smith and Skip Bayless, making bold statements and incorrect predictions:

![Video of Sports Pundits, Stephen A. Smith and Skip Bayless, Making Bold Statements and Incorrect Predictions. From: <https://www.youtube.com/watch?v=lTjBuEPcLlc>.](images/sportsPundits.mp4){width=100%}\

@@

Another reason why judgment methods are more widely used than actuarial methods is that so-called "experts" (and people in general) show [overconfidence](#sec-cognitiveBiasesOverconfidence) in their predictions—clinicians, experts, and humans in general think they are more accurate than they actually are.
We see this when examining their calibration; their predictions tend to be miscalibrated (this is also the case with fantasy football projections, as described in Section @sec-accuracyProjections).
For example, things they report with 80% confidence occur less than 80% of the time, an example of [overprecision](#sec-cognitiveBiasesOverconfidence) in their predictions.
Humans will sometimes be correct by chance, and they tend to mis-attribute that to their skill; humans tend to remember the successes and forget the failures.

### 2025-06-19 decision-making.qmd
20250619 - calibration accuracy of projections

Each of these possibilities is likely true to some degree.
First, individuals' predictions are unlikely to be highly accurate consistently.
Second, there are many players who are systematically *over*predicted (e.g., due to their injury) or *under*predicted (e.g., due to their becoming the starter after a teammate becomes injured, is traded, etc.)—an example of [overextremity miscalibration](#sec-calibration).
In general, it is likely for players who are projected to score more points to be overpredicted and for players who are projected to score fewer points to be underpredicted [PRESENT CALIBRATION STATS].
Third, the experts may interact and discuss with one another.
Interaction and discussion among experts may lead them to follow the herd and conform their projections to what each other predict.
This has been terms informational influence and may reflect the [anchoring and adjustment heuristic](#sec-heuristicsAnchoringAdjustment) [@Larrick2024].
In any case, they are able to see each other's projections and make change their projections, accordingly.

>>>>

Each of these possibilities is likely true to some degree.
First, individuals' predictions are unlikely to be highly accurate consistently.
Second, there are many players who are systematically *over*predicted (e.g., due to their injury) or *under*predicted (e.g., due to their becoming the starter after a teammate becomes injured, is traded, etc.)—an example of [overextremity miscalibration](#sec-calibration).
In general, it is likely for players who are projected to score more points to be overpredicted and for players who are projected to score fewer points to be underpredicted, as described in Section @sec-accuracyProjections.
Third, the experts may interact and discuss with one another.
Interaction and discussion among experts may lead them to follow the herd and conform their projections to what each other predict.
This has been terms informational influence and may reflect the [anchoring and adjustment heuristic](#sec-heuristicsAnchoringAdjustment) [@Larrick2024].
In any case, they are able to see each other's projections and make change their projections, accordingly.

### 2025-06-19 evaluating-prediction-accuracy.qmd
20250619 - ROC curve
20250619 - calibration accuracy of projections

@@

There are four general patterns of miscalibration: overextremity, underextremity, overprediction, and underprediction (see @fig-miscalibration).
*Overextremity* exists when the predicted probabilites are too close to the extremes (zero or one).
*Underextremity* exists when the predicted probabilities are too far away from the extremes.
*Overprediction* exists when the predicted probabilities are consistently greater than the observed probabilities.
*Underprediction* exists when the predicted probabilities are consistently less than the observed probabilities.
For a more thorough description of these types of miscalibration, see @Lindhiem2020.

@@

@@

>>>>

### Specify Options {#predictionAccuracySpecifyOptions}

```{r}
options(scipen = 999) # prevent scientific notation
```

@@

There are four general patterns of miscalibration: overextremity, underextremity, overprediction, and underprediction (see @fig-miscalibration).
*Overextremity* exists when the predicted probabilities are too close to the extremes (zero or one).
*Underextremity* exists when the predicted probabilities are too far away from the extremes.
*Overprediction* exists when the predicted probabilities are consistently greater than the observed probabilities.
*Underprediction* exists when the predicted probabilities are consistently less than the observed probabilities.
For a more thorough description of these types of miscalibration, see @Lindhiem2020.

@@

par(pty = "s")

@@

Below are estimates of projection accuracy and [calibration plots](#sec-calibrationPlot) for [seasonal](#sec-accuracyProjectionsSeasonal) and [weekly](#sec-accuracyProjectionsWeekly) projections.
Projections were poorly [calibrated](#sec-calibrationIndices) with respect to actual fantasy points.
In general, projected showed a modest tendency to underpredict performance at lower levels of projected points and a moderate-to-strong tendency overpredict performance at higher levels of projected points, an example of the overextremity form of [miscalibration](#sec-calibration).
As a reminder, the overextremity form of [miscalibration](#sec-calibration) is an example of the overprecision form of [overconfidence](#sec-cognitiveBiasesOverconfidence).
That is, projection sources appear to be [overconfident](#sec-cognitiveBiasesOverconfidence) in their projections of player performance.
